\subsection{Terms}
\begin{terminology}
    \begin{itemize}
        \item \textbf{Valuation:} Analytical process of determining current (or projected) worth of an asset, which has two components:
        \begin{itemize}
            \item Projected cash-flows
            \item Interest rate - determined by risk (uncertainty).
        \end{itemize}

        \item \textbf{Stock market:} The aggregation of buyers and sellers of stocks (i.e. shares), which represent ownership claims on businesses (i.e. public companies)

        \item \textbf{Financial Risk:} Uncertainty in a future payoff.
        \item \textbf{Pricing risk:} Determining an appropriate interest rate for a given uncertainty of a future cash flow. 

        
        \item \textbf{Variance of Returns:} The ith variance in the rate of return from a vector of return rates of a given ith stock, company, portfolio, etc.
        \[
        \sigma_i^2 = \text{Var}(\vec{R}_i), \quad \vec{R}_i = \begin{bmatrix}
        r_{t_1} \\
        r_{t_2} \\
        \vdots \\
        r_{t_m}
        \end{bmatrix}
        \]
        
        \item \textbf{Volatility ($\sigma_i$):} The standard deviation of the variance of return, which is a form of risk (i.e. uncertainty). Greater the volatility, greater the risk.
        
        \item \textbf{Modern Portfolio Theory:}
        \begin{itemize}
            \item Framework to assemble a portfolio of assets such that the expected return ($E[R]$) is maximized for a given level of risk.
            \item We want to maximize our return while minimizing volatility.
        \end{itemize}
    \end{itemize}            
\end{terminology}

\subsection{Capital Asset Pricing Model (CAPM)}
\begin{definition}
    \begin{equation}
        E[R_c] = r_f + \beta_c \left(E[R_{mp}] - r_f\right)
    \end{equation}
        
    \begin{itemize}
        \item $E[R_c]$: Expected rate of return for a company
        \item $r_f$: Risk-free rate
        \item $\beta_c$: Measure of risk for the company, systematic risk, related to market risk
        \item $E[R_{mp}]$: Expected rate of return of the market portfolio, represents the whole market
    \end{itemize}

    \vspace{1em}

    Relationships for $\beta$:
    \begin{equation}
        \beta_i = \frac{\sigma_{i, MP}}{\sigma^2_{MP}} = \rho_{i, MP} \frac{\sigma_i}{\sigma_{MP}}
    \end{equation}
    
    \begin{itemize}
        \item $\sigma_{i, MP}$: Covariance between $i^{th}$ company and market portfolio (MP)
        \item $\sigma^2_{MP}$: Variance of MP
        \item $\rho_{i, MP}$: Correlation of returns between $i^{th}$ company and MP
        \item $\sigma_i$: Volatility of $i^{th}$ company
        \item $\sigma_{MP}$: Volatility of MP
    \end{itemize}
\end{definition}

\subsection{Terms}
\begin{terminology}
    \begin{itemize}
        \item \textbf{Market Portfolio (MP):} Portfolio representing the whole market, often estimated through a stock index.
        
        \item \textbf{Systematic Risk:} Risk associated with the market as a whole, e.g. effect of economy on sales and stock value.
        
        \item \textbf{Idiosyncratic Risk:} Risk independent of the economy and specific to a company.
        
        \item \textbf{Arbitrage:} Taking advantage of a price difference between two or more markets to achieve a risk-free gain.
        
        \item \textbf{Forward Contract (Forwards):} An obligation to buy or sell a certain asset:
        \begin{itemize}
            \item At a specified price
            \item At a specified time
        \end{itemize}
        
        \item \textbf{Futures Contracts:} Similar to forwards except settled daily (not just at maturity), so they can be bought and sold, and are also traded on exchanges.
    \end{itemize}
\end{terminology}

\subsection{Replication (FIX)}
\begin{definition}
    \begin{itemize}
        \item Given present market price $P_{MP}$ will take on certain values if it goes up or down: $P_{MP+}$; $P_{MP-}$
            \begin{itemize}
                \item Probability of market going up is $X$, down is $(X-1)$ (interchangeable)
            \end{itemize}
        \item Given project/investment/etc. price $P_I$ will take on certain values depending on if market goes up or down: $P_{I+}$; $P_{I-}$
    \end{itemize}

    \vspace{1em}
    Want to find present value of project:

    \begin{itemize}
        \item Risk-free rate is $r_f$
    \end{itemize}

    \vspace{1em}

    The following networks are Market, $R_f$, and Project:

    \begin{tikzpicture}[->, >=stealth, auto, node distance=2.5cm, thick]

        \node (Market) {$P_{MP}$};
        \node (MarketUp) [above right=of Market] {$P_{MP+}$};
        \node (MarketDown) [below right=of Market] {$P_{MP-}$};
    
        \draw[->] (Market) -- (MarketUp) node[midway, above] {up};
        \draw[->] (Market) -- (MarketDown) node[midway, below] {down};
    
        \node (Rf) [right=4cm of Market] {$P_r = 1$};
        \node (RfPlus) [above right=of Rf] {$1 \times (1+r_f) = P_{r+}$};
        \node (RfMinus) [below right=of Rf] {$1 \times (1+r_f) = P_{r-}$};
        
        \draw[->] (Rf) -- (RfPlus);
        \draw[->] (Rf) -- (RfMinus);
        
        \node (Project) [right=4cm of Rf] {$P_I$};
        \node (ProjectUp) [above right=of Project] {$P_{I+}$};
        \node (ProjectDown) [below right=of Project] {$P_{I-}$};
    
        \draw[->] (Project) -- (ProjectUp) node[midway, above] {up};
        \draw[->] (Project) -- (ProjectDown) node[midway, below] {down};
    
    \end{tikzpicture}

    \begin{itemize}
        \item Replication wants to model a portfolio with the same risk-value as the project:
            \begin{itemize}
                \item $a$: \# of $MP$ shares
                \item $b$: \# of risk-free shares/bonds/etc.
            \end{itemize}
    \end{itemize}
    
    \begin{equation*}
        \begin{aligned}
            &\text{Up:} \quad a P_{MP+} + b P_{r+} = P_{I+} \\
            &\text{Down:} \quad a P_{MP-} + b P_{r-} = P_{I-}
        \end{aligned}
        \quad \text{Solve for } a, b
    \end{equation*}
    
    \[
    P_I = a \times P_{MP} + b \times P_r \quad \text{with} \quad P_r = 1
    \]
    
    \begin{itemize}
        \item Can also find $\beta$:
    \end{itemize}
    
    \[
    E[R_{MP}] = \frac{P_{MP+} X + P_{MP-} (X-1)}{P_{MP}}
    \]
    
    \[
    E[R_I] = \frac{P_{I+} X + P_{I-} (X-1)}{P_I}
    \]
    
    \[
    \therefore \quad \beta = \frac{E[R_I] - r_f}{E[R_{MP}] - r_f}
    \]

\end{definition}

\subsection{Forward Rate}
\begin{definition}
    Given rates for investments between $t=0$ and $t=t_1$, or $t=t_2$:
    \[
    r_{0,t_1}, \quad r_{0,t_2}
    \]

    \noindent The interest forward rate $t_1$ years from $t=0$ for a duration of $(t_2 - t_1)$ years is:
    
    \begin{equation}
        r_{t_1,t_2} = \frac{r_{0,t_2} \cdot t_2 - r_{0,t_1} \cdot t_1}{t_2 - t_1}
    \end{equation}            
\end{definition}