\documentclass{article}
\AtBeginDocument{\RenewCommandCopy\qty\SI}
\usepackage{style}
\title{ECE358 Cheatsheet}
\author{John Doe}
\lhead{ECE358}
\rhead{John Doe}

\begin{document}
\maketitle

\tableofcontents

\listoffigures

\listoftables

Read the textbook for this course. 

\section{Course Tips}
\begin{intuition}
    \begin{itemize}
        \item Go to ECE345 sessions to catch up if you miss a lecture since exact same content. Tutorials do more examples. 
        \item Homeworks are more difficult than the midterm and exam.
        \item Open CLRS Book: Open book, electronic notes, and handouts are good. 
        \item Do not use AI when doing HW, as this is great practice for midterms/finals.
    \end{itemize}
\end{intuition}

\section{Preliminaries}
\input{00_Lectures/00_0_Preliminaries.tex}
\newpage

% W1
\section{Asymptotics (Ch. 3.1-2 pg. 50-63, L2)} 
\input{00_Lectures/00_Asymptotics.tex}
\newpage

\section{Logarithms, Summations (L7)} % DONE
\input{00_Lectures/01_Logarithms_Summations.tex}
\newpage

\section{Induction, Contradiction (L3)} % DONE
\input{00_Lectures/02_Induction_Contradiction.tex}
\newpage

% W2
\section{Recurrences (Ch. 2.3, L4)} % DONE
\input{00_Lectures/03_Recurrences.tex}
\newpage

\section{Graphs, Trees (Ap. B.4-5, L6)} % DONE
\input{00_Lectures/04_Graphs_Trees.tex}
\newpage

\section{Permutations, Combinations (Ap. C.1, L5)} % DONE
\input{00_Lectures/05_Permutations_Combinations.tex}
\newpage

\section{Probability (Ap. C.2, L8)} %DONE
\input{00_Lectures/06_Probability.tex}
\newpage

% 5 LECTURES ^ 

\section{Heaps, Heapsort (Ch. 6, L9)} % DONE w/o textbook (TB)
\input{00_Lectures/07_Heaps_Heapsort.tex}
\newpage

\section{Quicksort (Ch. 7, L10)} % DONE except WS (formal) and AC.
\input{00_Lectures/08_Quicksort.tex}
\newpage

\section{Counting sort, Radix sort (Ch. 8)}
\input{00_Lectures/09_CountingSort_RadixSort.tex}
\newpage

% 4 LECTURES ^

\section{Selection sort, Binary search trees (Ch. 12)}
\input{00_Lectures/10_SelectionSort_BinarySearchTrees.tex}
\newpage

\section{Red black trees (Ch. 13)}
\input{00_Lectures/11_Red_Black_Trees.tex}
\newpage

% 3 LECTURES ^ 

\section{Hash tables, Hashing (Ch. 11)}
\input{00_Lectures/12_HashTables_Hashing.tex}
\newpage

% 1 LECTURE ^

\section{Dynamic programming (Ch. 14)}
\input{00_Lectures/13_Dynamic_Programming.tex}
\newpage

% 2 LECTURES ^ 

\section{Greedy algorithms (Ch. 15)} % MIDTERM CUT
\input{00_Lectures/14_Greedy_Algorithms.tex}
\newpage

% 2 LECTURES ^

\section{Amortized analysis (Ch. 16)}
\input{00_Lectures/15_Amortized_Analysis.tex}
\newpage

\section{Splay trees}
\input{00_Lectures/16_Splay_Trees.tex}
\newpage

% 3 LECTURES ^

\section{Graph algorithms (Ch. 20)}
\input{00_Lectures/17_Graph_Algorithms.tex}
\newpage

% 1 LECTURE ^

\section{Minimum spanning trees (Ch. 21)}
\input{00_Lectures/18_Minimum_Spanning_Trees.tex}
\newpage

% 1 LECTURE ^

\section{Shortest paths (Ch. 22)}
\input{00_Lectures/19_Shortest_Paths.tex}
\newpage

% 2 LECTURES ^

\section{Maximum flow (Ch. 24)}
\input{00_Lectures/20_Maximum_Flow.tex}
\newpage

% 2 LECTURES ^

\section{History of computation}
\input{00_Lectures/21_History_of_Computation.tex}
\newpage

% 1 LECTURE ^

\section{P, NP, and NPC introduction (Ch. 34)}
\input{00_Lectures/22_P_NP_NPC_Introduction.tex}
\newpage

\section{NP Completeness (NPC) (Ch. 34)} 
\input{00_Lectures/23_NPC.tex}

% 5 LECTURES ^ 

\end{document}