\documentclass{article}
\AtBeginDocument{\RenewCommandCopy\qty\SI}
\usepackage{style}
\title{ECE367 Cheatsheet}
\author{John Doe}
\lhead{ECE367}
\rhead{John Doe}

\begin{document}
\maketitle

\tableofcontents

\listoffigures

\listoftables

\section{QA}
\begin{intuition}
    \textbf{Optional” problems:} Optional problems provide extra practice or introduce interesting connections or extensions. 
    \begin{itemize}
        \item They need not be turned in. We will not grade them, but we will assume you have reviewed and understood the solutions to the optional problems when designing the exams. 
    \end{itemize}
\end{intuition}

\section{Vectors, Norms, Inner Products (Ch. 2.1-2.2)}
\input{00_Lectures/W1.tex}
\newpage

\section{Orthogonal Decomposition, Projecting onto Subspaces, Gram-Schmidt, QR Decomposition, Projection onto Affine Sets, Hyperplanes and Half-Spaces (Ch. 2.2-2.3)}
\input{00_Lectures/W2.tex}
\newpage

\section{Problem set 1}
\input{00_Lectures/PS1.tex}
\newpage

\section{Non-Euclidean Projection, Functions, Gradients and Hessians (Ch. 2.3-2.4)}
\input{00_Lectures/W3.tex}
\newpage

\section{Matrices, Range, Null Space, Eigenvalues, Eigenvectors, Matrix Diagonalization (Ch. 3.1-3.5)}
\input{00_Lectures/W4.tex}
\newpage

\section{Problem set 2}
\input{00_Lectures/PS2.tex}
\newpage

\section{Symmetric Matrices, Orthogonal Matrices, Spectral Decomposition, Positive Semidefinite Matrices, Ellipsoids (Ch. 4.1-4.4)}
\input{00_Lectures/W5.tex}
\newpage

\section{Singular Value Decomposition, Principal Component Analysis (Ch. 5.1, 5.3.2)}
\input{00_Lectures/W6.tex}
\newpage

\section{Interpretations of SVD, Low-Rank Approximation (Ch. 5.2-5.3.1)}
\input{00_Lectures/W7.tex}
\newpage

\section{Least Squares, Overdetermined and Underdetermined Linear Equations (Ch. 6.1-6.4)}
\input{00_Lectures/W8.tex}
\newpage

\section{Regularized Least-Squares, Convex Sets and Convex Functions (Ch. 6.7.3, 8.1-8.4)}
\input{00_Lectures/W9.tex}
\newpage

\section{Lagrangian Method for Constrained Optimization, Linear Programming and Quadratic Programming (Ch. 8.5, 9.1-9.6)}
\input{00_Lectures/W10.tex}
\newpage

\section{Numerical Algorithms for Unconstrained and Constrained Optimization (Ch. 12.1-12.3)}
\input{00_Lectures/W11.tex}

\end{document}