\documentclass{article}
\AtBeginDocument{\RenewCommandCopy\qty\SI}
\usepackage{style}
\title{ECE355 Cheatsheet}
\author{John Doe}
\lhead{ECE355}
\rhead{John Doe}

\begin{document}
\maketitle

\tableofcontents

\listoffigures

\listoftables

\section*{Tips}
\begin{intuition}
    \begin{itemize}
        \item May diverge from textbook, but only responsible for lecture content.
        \item Tutorials: Review of last week's topics and assigned problems. 
        \item Piazza for asking questions.
        \item ISM: Investigate topic of interest that uses signals or systems with 10 pages that are reference, explain concepts in your own way.
        \item Quiz every week except for term tests. 
        \item 30 minutes, appears Tuesday morning and ends Tuesday night. 
        \item Easier than usual questions that tests understanding. 
        \item Open book with MC, numerical answer. 
    \end{itemize}
\end{intuition}

\section*{TT1}
\begin{intuition}
    \begin{itemize}
        \item Sketch the signal if the signal is complicated to help with finding the answer. 
        \item Impaginary part is only the real part of the imaginary part. 
        \item LTI systems take linear combinations of inputs. 
        \item Really pays off to do the HW since he goes through the past HW and makes the TT1 slightly different. 
        \item Trick questions BE CAREFUL. 
        \item If you have an infinite signal and a finite signal, then use commutativity of LTI to convolve the finite signal with the infinite signal to make the math easier. 
    \end{itemize}
\end{intuition}

\section{Mathematical Review}
\input{Lectures/00_Math.tex}
\newpage

\begin{center}
    \section*{Signals and General Systems}
\end{center}
\section{Continuous and discrete-time signals (Ch. 1.1)}
\input{Lectures/01_Continuous_and_discrete_time_signals.tex}
\newpage

\section{Time dilation, shifting (Ch. 1.2)}
\input{Lectures/02_Time_dilation_shifting.tex}
\newpage

\section{Complex exponential signals (Ch. 1.3)}
\input{Lectures/03_Complex_exponential_signals.tex}
\newpage

\section{Step and impulse functions (Ch. 1.4)}
\input{Lectures/04_Step_and_impulse_functions.tex}
\newpage

\section{General systems and basic properties (Ch. 1.5-6)}
\input{Lectures/05_General_systems_and_basic_properties.tex}
\newpage

\begin{center}
    \section*{Linear Time-Invariant Systems}
\end{center}
\section{DT Impulse response (Ch. 2.1)}
\input{Lectures/06_Impulse_response.tex}
\newpage

\section{DT Convolution (Ch. 2.1,2.3)}
\input{Lectures/07_Convolution_in_discrete_time.tex}
\input{Lectures/09_Properties_of_LTI_systems.tex}
\newpage

\section{CT Convolution and Properties of LTI systems (Ch. 2.2)}
\input{Lectures/08_Convolution_in_continuous_time.tex}
\newpage

\begin{center}
    \section*{Fourier Series and Fourier Transform Representations}
\end{center}
\section{CT Periodic signals and Fourier series}
\input{Lectures/10_Periodic_signals_and_Fourier_series_CT.tex}
\input{Lectures/11_Properties_of_Fourier_series.tex}
\newpage

\section{DT Periodic signals and Fourier series}
\input{Lectures/12_Periodic_signals_and_Fourier_series_DT.tex}
\newpage

\section{Response of LTI systems to periodic signals}
\input{Lectures/13_Response_of_LTI_systems_to_periodic_signals.tex}
\newpage

\section{Aperiodic signals and Fourier transform}
\input{Lectures/14_Aperiodic_signals_and_Fourier_transform.tex}
\newpage

\section{Fourier transform properties; time-frequency duality}
\input{Lectures/15_Fourier_transform_properties_timefrequency_duality.tex}
\newpage

\section*{Sampling}
\section{Modulation}
\input{Lectures/16_Modulation.tex}
\newpage
\section{Bandlimited signals}
\newpage

\section{The sampling theorem (Ch. 7.1)}
\newpage

\section{Reconstruction (Ch. 7.2)}
\newpage

\section*{Communication Systems}
\section{Amplitude modulation systems}
\newpage

\section{Envelope detection, coherent detection}
\newpage

\section{Single-sideband modulation}
\newpage

\section{Angle modulation}
\newpage

\section{Concepts of digital communication}

\end{document}